\section{Data Monitoring }(Chris and Tim?)

The software nature of the UTMOST provides a high level of opportunity for data monitoring and inspection. The lattice FPGA on the RX board can send small snippets of data via Gb ethernet to the DAQ machines which can be plotted as bandpasses, time series and data histograms via a web interface. Similarly once a second the UDP capture system sends 512 voltages from each channel to a ring buffer where a series of plots are created, again available for scrutiny via a web interface.

(INSERT histogram overview)

At the other extreme, it is possible to record large (10-120s) bursts of the PFB raw voltages to the SSD drives of the DAQ computers for offline processing. The software backend can either operate in real time on the real voltage streams or in an offline mode on the recorded voltages. The usefulness of this mode in debugging the software instrument cannot be understated. A real-time correlator cannot usually playback data, and thus cannot perform ``difference'' experiments or confirm the validity of new features on proven input data sets. During the commissioning data captured would often be played back dozens of times to debug the system.

When observing in FX correlation mode, a ``correlation triangle'' appears on a web interface which can be interrogated to display phase vs time for any baseline (see Figure 3) and used to update the instrumental delays.
Folded pulsar profiles are also shown `live'' in both independent modes and tied array beam modes. Figure 4 shows an observation of the millisecond pulsar PSR J0437-4715 observed in tied array beam mode.
